Eval expressions

### 2021-01-06 analysis/expressions.Rmd
Call site with one resolved expressions, to a value type.

@@

```{r}
widespread_expr <- E %>% group_by(ev_expr) %>% summarize(n_call_sites = n_distinct(src_ref), n_packages = n_distinct(ev_package))
```

>>>>

# Resolved expressions

Are expressions resolved to very diverse values or expressions?
If they are uniquely resolved and it is a value, then we can get rid of the `eval`.

```{r}

resolved_variety <- E %>% group_by(ev_expr, src_ref) %>% summarise(n = n_distinct(expr_resolved)) %>% arrange(desc(n)) 
resolved_variety %>% datatable()

nb_one_resolved <- resolved_variety %>% filter(n == 1) %>% nrow()

```

There are `r nb_one_resolved` call sites that are resolved to only one expression, out of `r nrow(resolved_variety)`.

We can now count how many of these call sites with only one resolved expression resolve to a value type.

```{r}
one_resolved_type <- E %>% group_by(src_ref) %>% mutate(n_resolved = n_distinct(expr_resolved)) %>% filter(n_resolved == 1) %>% ungroup() %>% select(src_ref, n_resolved, type) %>% distinct()

nb_one_resolved_type <- one_resolved_type %>% nrow()
```

`r nb_one_resolved_type` call sites resolved to one expression, of only one type.

```{r}
nb_value_type <- one_resolved_type %>% filter(type %in% c("character", "double", "integer", "logical", "NULL"))
```

There are `r nb_value_type` such call sites.

@@

```{r}
widespread_expr <- E %>% group_by(expr_resolved) %>% summarize(n_call_sites = n_distinct(src_ref), n_packages = n_distinct(ev_package))
```
